Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-09-09 analysis/report/effectiveness_report_comparemodels.Rmd
update model comparison report

  plot_effects <-
    ggplot(data = tidy_effects) +
    geom_point(aes(y=exp(estimate), x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_linerange(aes(ymin=exp(conf.low), ymax=exp(conf.high), x=term_midpoint, colour=model_name), position = position_dodge(width = 1.8))+
    geom_hline(aes(yintercept=1), colour='grey')+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(
      breaks = seq(0, 7*52, 14), 
      limits = c(min(tidy_effects$term_left), 20*7), 
      expand = c(0, 0)
    )+
    scale_y_log10(
    breaks=c(0.125, 0.167, 0.25, 0.333, 0.5, 0.667, 1, 1.5, 2, 3, 4, 6, 8),
    sec.axis = dup_axis(name="favours\n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
  )+
    scale_colour_brewer(type="qual", palette="Set2", guide=guide_legend(ncol=2))+
    labs(
      y="Hazard ratio",#\nChAdOx1 / BNT162b2",
      x="Days since vaccination",
      colour=NULL
     ) +
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  plot_spline <-
    ggplot(spline)+
    geom_hline(aes(yintercept=1), colour='grey')+
    geom_line(aes(x=tstop-1, y=hr, colour=model_name))+
    geom_ribbon(aes(x=tstop-1, ymin=hr.ll, ymax=hr.ul, fill=model_name), alpha=0.2, colour="transparent")+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_log10(
      breaks=c(0.125, 0.167, 0.25, 0.333, 0.5, 0.667, 1, 1.5, 2, 3, 4, 6, 8),
      sec.axis = dup_axis(name="favours\n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    scale_colour_brewer(type="qual", palette="Set2", guide=guide_legend(ncol=1))+
    scale_fill_brewer(type="qual", palette="Set2", guide="none")+
    labs(
      x = "Days since first dose",
      y = "Hazard ratio",
      colour = NULL, fill=NULL
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  plot_cmlinc <-
    ggplot(curves %>% filter(model=="3"))+
    geom_step(aes(x=tstop, y=1-survival, group=vax1_az_descr, colour=vax1_az_descr))+
    geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=1-survival.ll, ymax=1-survival.ul, group=vax1_az_descr, fill=vax1_az_descr), alpha=0.1)+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0)
    )+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x="Days since first dose",
      y="Adjusted survival",
      colour=NULL
    )+
    theme_bw()+
    theme(
      legend.position=c(0.95,.05),
      legend.justification = c(1,0),
      axis.text.x.top=element_text(hjust=0),

@@

  plot_diff <-
    ggplot(curves)+
    geom_hline(aes(yintercept=0, colour=model_name))+
    geom_step(aes(x=tstop, y=diff, colour=model_name))+
    geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=diff.ll, ymax=diff.ul, fill=model_name), alpha=0.1, colour="transparent")+
    facet_grid(cols=vars(timescale))+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0),
      sec.axis = dup_axis(name="Lower risk after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    #coord_cartesian(ylim= c(-5, 5))+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x=NULL,
      y="Difference\nin cumulative incidence",
      colour=NULL,
      fill=NULL
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y.left = element_line(colour = "black"),

@@

@@

cat("  \n\n")
print(glue("### COVID-19 A&E attendance"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("covidemergency")
print(glue("#### Cox"), "  \n")
print_plots_effects("covidemergency", "cox", "0")
print(glue("#### PLR, piecewise"), "  \n")
print_plots_effects("covidemergency", "plr", "0")
print(glue("#### PLR, spline"), "  \n")
print_plots_spline("covidemergency", "0")
print_plots_adjsurv("covidemergency", "0")
print_plots_diff("covidemergency", "0")

>>>>

  plot_effects <-
    ggplot(data = tidy_effects) +
    geom_point(aes(y=exp(estimate), x=term_midpoint), position = position_dodge(width = 1.8))+
    geom_linerange(aes(ymin=exp(conf.low), ymax=exp(conf.high), x=term_midpoint), position = position_dodge(width = 1.8))+
    geom_hline(aes(yintercept=1), colour='grey')+
    facet_grid(rows=vars(timescale), cols=vars(model_name))+
    scale_x_continuous(
      breaks = seq(0, 7*52, 14), 
      limits = c(min(tidy_effects$term_left), 20*7), 
      expand = c(0, 0)
    )+
    scale_y_log10(
    breaks=c(0.125, 0.167, 0.25, 0.333, 0.5, 0.667, 1, 1.5, 2, 3, 4, 6, 8),
    sec.axis = dup_axis(name="favours\n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
  )+
    labs(
      y="Hazard ratio",#\nChAdOx1 / BNT162b2",
      x="Days since vaccination",
      colour=NULL
     ) +
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  plot_spline <-
    ggplot(spline)+
    geom_hline(aes(yintercept=1), colour='grey')+
    geom_line(aes(x=tstop-1, y=hr))+
    geom_ribbon(aes(x=tstop-1, ymin=hr.ll, ymax=hr.ul), alpha=0.2, colour="transparent")+
    facet_grid(rows=vars(timescale), cols=vars(model_name))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_log10(
      breaks=c(0.125, 0.167, 0.25, 0.333, 0.5, 0.667, 1, 1.5, 2, 3, 4, 6, 8),
      sec.axis = dup_axis(name="favours\n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    labs(
      x = "Days since first dose",
      y = "Hazard ratio",
      colour = NULL, fill=NULL
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),

@@

  plot_cmlinc <-
    ggplot(curves %>% filter(model=="3"))+
    geom_step(aes(x=tstop, y=1-survival, group=vax1_az_descr, colour=vax1_az_descr))+
    geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=1-survival.ll, ymax=1-survival.ul, group=vax1_az_descr, fill=vax1_az_descr), alpha=0.1)+
    facet_grid(rows=vars(timescale), cols=vars(model_name))+
    scale_x_continuous(
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0)
    )+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x="Days since first dose",
      y="Adjusted survival",
      colour=NULL
    )+
    theme_bw()+
    theme(
      legend.position=c(0.95,.05),
      legend.justification = c(1,0),
      axis.text.x.top=element_text(hjust=0),

@@

  plot_diff <-
    ggplot(curves)+
    geom_hline(aes(yintercept=0))+
    geom_step(aes(x=tstop, y=diff))+
    geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=diff.ll, ymax=diff.ul), alpha=0.1, colour="transparent")+
    facet_grid(rows=vars(timescale), cols=vars(model_name))+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0),
      sec.axis = dup_axis(name="Lower risk after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    labs(
      x=NULL,
      y="Difference\nin cumulative incidence"
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y.left = element_line(colour = "black"),

@@

      plot.title = element_text(hjust = 0),
      plot.title.position = "plot",
      plot.caption.position = "plot",
      plot.caption = element_text(hjust = 0, face= "italic"),
      legend.position = "bottom"

@@

cat("  \n\n")
# print(glue("### COVID-19 A&E attendance"), "  \n")
# print(glue("#### Unadjusted"), "  \n")
# print_plots_km("covidemergency")
# print(glue("#### Cox"), "  \n")
# print_plots_effects("covidemergency", "cox", "0")
# print(glue("#### PLR, piecewise"), "  \n")
# print_plots_effects("covidemergency", "plr", "0")
# print(glue("#### PLR, spline"), "  \n")
# print_plots_spline("covidemergency", "0")
# print_plots_adjsurv("covidemergency", "0")
# print_plots_diff("covidemergency", "0")
